---
title: "Reproducible Research: Peer Assessment 1"
author: "Akshika Baluapuri"
date: "April 25, 2019"
output: html_document
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Q1 = Code for reading in the dataset and/or processing the data


```{r echo=TRUE}
library(lattice)
act <- read.csv("repdata_data_activity1/activity.csv")
```


## Q2 = Histogram of the total number of steps taken each day
```{r echo=TRUE}
active <- aggregate(steps ~ date, data =  act, sum, na.rm =TRUE)
 hist(active$steps, col = "blue")

```


## Q3 = Mean and median number of steps taken each day
```{r echo=TRUE}
 meanactive <- mean(active$steps)
 maxactive <- max(active$steps)
```

## Q4 = Time series plot of the average number of steps taken
```{r echo=TRUE}
 avgstep <- aggregate(steps ~ interval , data= act, mean, na.rm = TRUE)
 plot(avgstep, type = "l")
 
```
 
## Q5 =The 5-minute interval that, on average, contains the maximum number of steps
```{r echo=TRUE}
stepmax <-  avgstep[which.max(avgstep$steps),]$interval
```
## Q6 = Code to describe and show a strategy for imputing missing data
```{r echo=TRUE}
na <- sum(is.na(act$steps))
```

##Q7 = Histogram of the total number of steps taken each day after missing values are imputed
```{r echo=TRUE}
stepeachd <- function(interval){
  avgstep[avgstep$interval == interval,]$steps
}

act1 <- act
for (i in 1:nrow(act1)) {
  if(is.na(act1[i,]$steps)){
    act1[i,]$steps <- stepeachd(act1[i,]$interval)
  }
  
}


active1 <- aggregate(steps ~ date, data =  act1, sum)
hist(active1$steps, col = "blue")

meanactive1 <- mean(active1$steps)
maxactive1 <- max(active1$steps)
```
## Q8 = Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r echo=TRUE}
act1$date <- as.Date(strptime(act1$date, format = "%Y-%m-%d"))
act1$day <- weekdays(act1$date)
for (i in 1:nrow(act1)) {
  if(act1[i,]$day %in% c("Satuaday", "Sunday")){
    act1[i,]$day <- "Weekend"
  }
    else{
      
      act1[i,]$day <- "Weekday"
    }
  }

stepday <- aggregate(act1$steps ~ act1$interval + act1$day, act1, mean )
names(stepday) <- c("interval", "day", "steps")
xyplot(steps ~ interval | day ,data =  stepday, type = "l", layout(c(1,2)
                  ))

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
